---
title: "Dashboard"
format:
  dashboard: 
    orientation: columns
---

## Column {width="20%"}

### Row {height="55%"}

```{r, install_packages}
#| echo: false
#| include: false
library(tidyverse)
```

```{r, load_data}
#| echo: false
#| include: false

raw_data <- readRDS("Data/2025-02-28_datastore.rds")


cleaned_data <-
  raw_data %>%
  # Select relevant columns
  select(
    CSNumber,
    ServiceName,
    CareService,
    Subtype,
    MinGrade,
    Last_inspection_Date,
    NumberStaff,
    Registered_Places,
    starts_with("KQ"),
    -ends_with("change"),
    starts_with("Complaints_upheld_"),
    starts_with("Enforcements_issued_"),
    starts_with("any_requirements_")
  ) %>%
  # Remove empty service ID numbers
  filter(CSNumber != "") %>%
  # Pivot grade categories in order to revalue grades as strings
  pivot_longer(cols = starts_with("KQ"),
               names_to = "Key Question",
               values_to = "Grade") %>%
  mutate(
    Grade = case_match(
      Grade,
      NA ~ "No grade yet",
      1 ~ "Unsatisfactory",
      2 ~ "Weak",
      3 ~ "Adequate",
      4 ~ "Good",
      5 ~ "Very good",
      6 ~ "Excellent"
    )
  ) %>%
  pivot_wider(names_from = `Key Question`, values_from = "Grade") %>%
  # Convert encoding to prevent special characters in strings
  mutate_if(is.character, function(col)
    iconv(col, to = "UTF-8"))

datastore <- 
  cleaned_data %>% 
  mutate(
    # Custom name for service combining with ID number
    service = paste0(ServiceName, " - ", CSNumber),
    # Keep numeric mingrade for conditional queries
    MinGrade_numeric = MinGrade,
    # Converting minimum grade to strings too
    MinGrade = case_match(
      MinGrade,
      NA ~ "No grade yet",
      1 ~ "Unsatisfactory",
      2 ~ "Weak",
      3 ~ "Adequate",
      4 ~ "Good",
      5 ~ "Very good",
      6 ~ "Excellent"
    ),
    # Convert date fields to dates
    Last_inspection_Date = as.Date(Last_inspection_Date, format("%d/%m/%Y")),
    months_since_inspection = interval(Last_inspection_Date, Sys.Date()) %/% months(1),
    days_since_inspection = ifelse(
      months_since_inspection < 1,
      lubridate::time_length(difftime(Sys.Date(), Last_inspection_Date), "days"),
      NA
    ),
    years_since_inspection = lubridate::time_length(difftime(Sys.Date(), Last_inspection_Date), "years"),
    staff_per_place = ifelse(
      Registered_Places == 0 |
        NumberStaff == 0,
      NA,
      NumberStaff / Registered_Places
    )
  ) |> 
  # Just 5 services of varying grades to make loading times quicker for now
  group_by(MinGrade_numeric, CareService, Subtype) |> 
  slice(1:2)

# Specify order of grades in minimum grade as factor
datastore$MinGrade <- factor(
datastore$MinGrade,
  levels =  c(
    "Unsatisfactory",
    "Weak",
    "Adequate",
    "Good",
    "Very good",
    "Excellent",
    "No grade yet"
  )
)
```


```{r, sendtoojs}
#| echo: false
#| include: false
ojs_define(datastore = datastore)
```

```{ojs}
//| echo: false
//| output: false

// Load tidyverse-equivalent OJS library for later reshaping and visualising
import { aq, op } from '@uwdata/arquero'
import { Plot } from "@observablehq/plot"

// Transpose data to make it useable in ojs inputs
datastore_transposed = transpose(datastore)
```


```{ojs}
// Create search box of service names
viewof search = Inputs.search(datastore_transposed, {placeholder: "Type to find a service",
width: 150,
height: 10})

// Create drop down menu of service names
viewof items = Inputs.table(search, {
columns: ["service"],
header: {service: "Select:"},
width: 300,
height: 250,
required: true,
value: search, 
multiple: false})
```


```{ojs}
//| echo: false
//| output: false

// Create function to output selected service name and return select service if none selected
function return_name() {
  var name = "Select a service"
  if(items === null) {
    return name
  } else {
    return items.service
  }
}

service_selected_name = return_name()

// Create function to output row of selected service
function filtered_df() {
  var name = "Select a service"
  if(items === null) {
    return name
  } else {
    return items
  }
}

service_selected = filtered_df()
```

### Row {height="33%"}

::: {.callout-note appearance="minimal"}
## Disclaimer
This dashboard is not affiliated with or supported by the Care Inspectorate. It contains public sector information licensed under the Open Government Licence v3.0. 

[Data source](https://www.careinspectorate.com/index.php/publications-statistics/93-public/datastore)
:::

### Row {height="12%"}

<SPAN STYLE="font-size:9.0pt">
Last refreshed: `r format(Sys.time(), "%d %b %Y %X")` <br>
Data as at: `r format(as.Date(substr(list.files("Data")[[1]], 0, 10)), "%d %b %Y")`
</SPAN> 

# Overview

```{ojs}
//| echo: false
//| output: false

// Use arquero to create dynamic values included in value boxes
mytable = aq.table(datastore)

// Create filtered table for same service type for comparison calculations
selected_service_compare = mytable
  .params({
  // define parameters
    selected_CareService: service_selected.CareService,
    selected_Subtype: service_selected.Subtype
  })
  // filter to only include services of the same type
  .filter((d, $) => op.includes($.selected_CareService, d.CareService) &&
  op.includes($.selected_Subtype, d.Subtype))
```

### Row 

::: {.valuebox icon="card-list" color="white"}
<div class="value-box-title">
Service type
</div>

<div class="value-box-value">

```{ojs}
//| echo: false
//| output: false


// Check if subtype blank
service_name_check = {
 if(service_selected.Subtype === "") {
   return service_selected.CareService;
    } else {
    return (service_selected.CareService + " - " + service_selected.Subtype);
  }
}


// SELECTED SERVICE TYPE
selected_serv_type  = {
  if (service_selected.CareService) {
    return service_name_check;
  } else {
    return "Select a service";
  }
}
```

`{ojs}  selected_serv_type`

</div>

```{ojs}
//| echo: false
//| output: false

// NUMBERS OF SERVICES OF SAME TYPE
number_services_same_type = selected_service_compare
  .rollup({
      count: op.count()
  })
   .objects()[0].count
   
// NUMBERS OF SERVICES WITH NO GRADE
number_services_same_type_no_grade = selected_service_compare
 .filter(d => op.includes("No grade yet", d.MinGrade))
  .rollup({
      count: op.count()
  })
   .objects()[0].count
   
// TEXT STRING SUBTITLE
selected_serv_type_subtitle  = {
  if (service_selected.CareService) {
    return ( "There are " + number_services_same_type + " of these services, " + number_services_same_type_no_grade + " have not yet received grades" );
  } else {
    return "";
  }
}
```

`{ojs} selected_serv_type_subtitle`

:::

::: {.valuebox icon="house-heart-fill" color="white"}
<div class="value-box-title">
Lowest grade
</div>

<div class="value-box-value">

```{ojs}
//| echo: false
//| output: false

// SELECTED SERVICE TYPE
selected_serv_grade  = {
  if (service_selected.CareService) {
    return (service_selected.MinGrade);
  } else {
    return "Select a service";
  }
}
```

`{ojs} selected_serv_grade`

</div>

```{ojs}
//| echo: false
//| output: false

// PERCENTAGE OF SERVICES WITH SAME GRADE
perc_services_same_grade = selected_service_compare
.params({
  // define parameters
    selected_MinGrade: service_selected.MinGrade
  })
  // first filter out those that don't have any grades
  .filter(d  => d.MinGrade_numeric >= 1)
  // group by each grade
  .groupby("MinGrade")
  // calculate counts of services with each mingrade
  .rollup({
      count: op.count()
  })
  // create new column for proportion of services with each grade
  .derive({ percent: d => op.round((d.count / op.sum(d.count) || 0)*100) }) // include `|| 0` in case sum is zero
  // filter out match selected grade
  .filter((d, $) => op.includes($.selected_MinGrade, d.MinGrade))
  // pull out percent value
   .objects()[0].percent
  
   
// PERCENTAGE OF SERVICES WITH HIGHER GRADE
perc_services_higher_grade = selected_service_compare
.params({
  // define parameters
     selected_MinGrade_numeric: service_selected.MinGrade_numeric
  })
  // first filter out those that don't have any grades
  .filter(d  => d.MinGrade_numeric >= 1)
  // group by each grade
  .groupby("MinGrade_numeric")
  // calculate counts of services with each mingrade
  .rollup({
      count: op.count()
  })
  // create new column for proportion of services with each grade
  .derive({ percent: d => op.round((d.count / op.sum(d.count) || 0)*100) }) // include `|| 0` in case sum is zero
  // Ungroup by minimum grade
  .ungroup()
  // filter out match selected grade
  .filter((d, $) => d.MinGrade_numeric > $.selected_MinGrade_numeric)
  .derive({total: d => op.sum(d.percent)})
  // pull out total value
  .object(1)?.total ?? 0
   
// TEXT STRING SUBTITLE
selected_serv_grade_subtitle  = {
  if (service_selected.CareService) {
    return ( "Same as " + perc_services_same_grade + "% of services of the same type, whilst " + perc_services_higher_grade + "% have a higher minimum grade" );
  } else {
    return "";
  }
}
```

`{ojs} selected_serv_grade_subtitle`

:::

::: {.valuebox icon="calendar-event-fill" color="white"}
<div class="value-box-title">
Last inspected
</div>

```{ojs}
//| echo: false
//| output: false

// First check if been inspected 
inspection_check = {
  if(service_selected.months_since_inspection >=0) {
    return (service_selected.months_since_inspection + " month(s) since last inspection");
  } else {
    return "No inspection yet";
  }
}

// SELECTED SERVICE LAST INSPECTION
selected_serv_last_inspection  = {
  if (service_selected.CareService) {
    return inspection_check; 
  } else {
    return "Select a service";
  }
}
```

<div class="value-box-value">

`{ojs} selected_serv_last_inspection`

</div>

```{ojs}
//| echo: false
//| output: false

// MEDIAN TIME SINCE LAST INSPECTION
median_time_last_inspection = selected_service_compare 
  // filter out those that haven't yet been inspected
 .filter(d => d.months_since_inspection >= 0)
  .rollup({
    count: op.count(),
    median_months_since_inspection: op.median('months_since_inspection')
   })
   .objects()[0].median_months_since_inspection
   
// TEXT STRING SUBTITLE
selected_serv_last_inspection_subtitle  = {
  if (service_selected.CareService) {
    return "The average (median) time since the last inspection for services of this type is " + median_time_last_inspection + " month(s)";
  } else{
    return "";
  }
}
```

`{ojs} selected_serv_last_inspection_subtitle`

:::


### Row 


::: {.valuebox icon="people-fill" color="white"}

<div class="value-box-title">
Number of staff
</div>

```{ojs}
//| echo: false
//| output: false

// First check they have staff
staff_check = {
  if(service_selected.staff_per_place >=0) {
    return (service_selected.staff_per_place.toFixed(2) + " staff per registered place");
  } else {
    return "No staff recorded";
  }
}

// SELECTED SERVICE LAST INSPECTION
staff_per_place  = {
  if (service_selected.CareService) {
    return staff_check; 
  } else {
    return "Select a service";
  }
}
```

<div class="value-box-value">

`{ojs} staff_per_place `

</div>

```{ojs}
//| echo: false
//| output: false

// MEDIAN STAFF PER REG PLACE
median_staff = selected_service_compare 
 .filter(d => d.staff_per_place > 0)
  .rollup({
    count: op.count(),
    median_staff_per_place: op.median('staff_per_place')
   })
  .objects()[0]?.median_staff_per_place ?? "No staff recorded"
  
  
// First check for those that are undefined as all services have had no complaints
staff_undefined_check = {
  if(median_staff !== "No staff recorded"){
    return "The average (median) number of staff per registered place for services of this type is " + median_staff.toFixed(2);
  } else {
    return "No services of this type had any staff recorded";
  }
}
  
// TEXT STRING SUBTITLE
median_staff_subtitle  = {
  if (service_selected.CareService) {
    return staff_undefined_check;
  } else{
    return "";
  }
}
```

`{ojs} median_staff_subtitle`

:::

::: {.valuebox icon="chat-right-dots-fill" color="white"}

<div class="value-box-title">
Upheld complaints
</div>

```{ojs}
//| echo: false
//| output: false

// First check there were complaints in year 2425
complaints_check = {
  if(service_selected.Complaints_upheld_2425 >=0) {
    return (service_selected.Complaints_upheld_2425 + " upheld complaint(s) between 1 April 2024 and 31 March 2025");
  } else {
    return "No upheld complaints between 1 April 2024 and 31 March 2025";
  }
}

// SELECTED SERVICE COMPLAINTS
complaints  = {
  if (service_selected.CareService) {
    return complaints_check ; 
  } else {
    return "Select a service";
  }
}
```

<div class="value-box-value">

`{ojs} complaints`

</div>

```{ojs}
//| echo: false
//| output: false

// PERCENTAGE OF SERVICES WITH ATLEAST 1 UPHELD COMPLAINT
perc_services_complaint = selected_service_compare
  // group by each grade
  .groupby("Complaints_upheld_2425")
  // calculate counts of services with all the varying numbers of upheld complaints
  .rollup({
      count: op.count()
  })
  // create new column for proportion of services with each number of complaints
  .derive({ percent: d => op.round((d.count / op.sum(d.count) || 0)*100) }) // include `|| 0` in case sum is zero
  // Ungroup by number of complaints
  .ungroup()
  // filter out anything less than 1
  .filter((d) => d.Complaints_upheld_2425 >= 1)
  .derive({total: d => op.sum(d.percent)})
  // pull out total value
  .objects()[0]?.total ?? 0

// First check for those that are undefined as all services have had no complaints
complaints_undefined_check = {
  if(perc_services_complaint !== 0){
    return perc_services_complaint + "% of services of this type had at least one upheld complaint between 1 April 2024 and 31 March 2025";
  } else {
    return "No services of this type had at least one upheld complaint between 1 April 2024 and 31 March 2025";
  }
}
  
// TEXT STRING SUBTITLE
complaints_subtitle  = {
  if (service_selected.CareService) {
    return complaints_undefined_check;
  } else{
    return "";
  }
}
```

`{ojs} complaints_subtitle`

:::


::: {.valuebox icon="clipboard2-check-fill" color="white"}

<div class="value-box-title">
Requirements from inspection
</div>

```{ojs}
//| echo: false
//| output: false

// First check there were requirements in year 2425
requirements_check = {
  if(service_selected.any_requirements_2425 === "Yes") {
    return ("This service had requirement(s) from inspections between 1 April 2024 and 31 March 2025");
  } else  if(service_selected.any_requirements_2425 === "Inspected but no requirements") {
    return "This service had no requirement(s) from inspections between 1 April 2024 and 31 March 2025";
  } else {
  return "This service was not inspected between 1 April 2024 and 31 March 2025"
  }
}

// SELECTED SERVICE REQUIREMENTS
requirements  = {
  if (service_selected.CareService) {
    return requirements_check ; 
  } else {
    return "Select a service";
  }
}
```

<div class="value-box-value">

`{ojs} requirements`

</div>

```{ojs}
//| echo: false
//| output: false

// PERCENTAGE OF SERVICES WITH ATLEAST 1 REQUIREMENT (OF THOSE THAT HAD BEEN INSPECTED)
perc_services_requirement = selected_service_compare
  // First filter out those that have not been inspected (i.e. blank field)
  .filter((d) => d.any_requirements_2425 !== "")
  // group by each grade
  .groupby("any_requirements_2425")
  // calculate counts of services with all the varying categories of requirements (yes, inspected but none, and blank)
  .rollup({
      count: op.count()
  })
  // create new column for proportion of services with each number of requirements
  .derive({ percent: d => op.round((d.count / op.sum(d.count) || 0)*100) }) // include `|| 0` in case sum is zero
  // Ungroup by number of requirements
  .ungroup()
  // filter only those that are "Yes"
  .filter((d) => d.any_requirements_2425 === "Yes")
  .derive({total: d => op.sum(d.percent)})
  // pull out total value
  .objects()[0]?.total ?? 0

// First check for those that are undefined as all services have had no complaints
requirements_undefined_check = {
  if(perc_services_requirement !== 0){
    return perc_services_requirement + "% of services of this type that had been inspected between 1 April 2024 and 31 March 2025 had at least one requirement";
  } else {
    return "No services of this type that had been inspected between 1 April 2024 and 31 March 2025 had any requirements";
  }
}
  
// TEXT STRING SUBTITLE
requirements_subtitle  = {
  if (service_selected.CareService) {
    return requirements_undefined_check;
  } else{
    return "";
  }
}
```

`{ojs} requirements_subtitle`

:::


# Grades

```{ojs}
//| echo: false
//| output: false

// Grade levels (in order)
grades = ["Unsatisfactory", "Weak", "Adequate", "Good", "Very good", "Excellent", "No grade yet"]

// --- 1. Selected Service Plot Data ---
selected_wrangled = aq.from([service_selected]) // Wrap in array because service_selected is one row
  .fold(Object.keys(service_selected).filter(d => d.startsWith("KQ")), { as: ["kq", "grade"] })
  .groupby("kq", "grade")
  .rollup({ count: op.count() })
  .ungroup("grade")
  // Mapping KQ codes to readable labels
  .derive({
    kq_label: (d) => op.recode(d.kq, { 'KQ_Support_Wellbeing': 'How well do we support people’s wellbeing?','KQ_Staff_Team': 'How good is our staff team?', 'KQ_Setting': 'How good is our setting?', 'KQ_Leadership': 'How good is our leadership?', 'KQ_Care_Play_and_Learning': 'How good is our care, play and learning?', 'KQ_Care_and_Support_Planning': 'How well is our care and support planned?'}, '?')
  })
  
// --- 2. Comparison Group Data ---
comparison_wrangled = selected_service_compare
.params({
  // define parameters
    selected_KQ_Care_and_Support_Planning: service_selected.KQ_Care_and_Support_Planning,
    selected_KQ_Support_Wellbeing: service_selected.KQ_Support_Wellbeing,
    selected_KQ_Staff_Team: service_selected.KQ_Staff_Team,
    selected_KQ_Setting: service_selected.KQ_Setting,
    selected_KQ_Leadership: service_selected.KQ_Leadership,
    selected_KQ_Care_Play_and_Learning: service_selected.KQ_Care_Play_and_Learning
    
  })
  .fold(Object.keys(service_selected).filter(d => d.startsWith("KQ")), { as: ["kq", "grade"] })
  .groupby("kq", "grade")
  .rollup({ count: op.count() })
  .filter((d) => d.grade !== "No grade yet")
  .ungroup()
  // Mapping KQ codes to readable labels
  .derive({
    kq_label: (d) => op.recode(d.kq, { 'KQ_Support_Wellbeing': 'How well do we support people’s wellbeing?','KQ_Staff_Team': 'How good is our staff team?', 'KQ_Setting': 'How good is our setting?', 'KQ_Leadership': 'How good is our leadership?', 'KQ_Care_Play_and_Learning': 'How good is our care, play and learning?', 'KQ_Care_and_Support_Planning': 'How well is our care and support planned?'}, '?')
  })
  // Create numbered equivalent of grades for orderby later
  .derive({
  grade_value: (d) => op.recode(d.grade, { 'Unsatisfactory': 1,'Weak': 2, 'Adequate': 3, 'Good': 4, 'Very good': 5, 'Excellent': 6}, '?')
})
  .groupby("kq")
  .derive({
    proportion: d => d.count / op.sum(d.count)
  })
  .orderby("kq_label", "grade_value")
  .derive({
  // Calculate cumsum
    cumsum: aq.rolling(d => op.sum(d.proportion))
  })
    // calculate proportion of services GREATER THAN so it's 1 minus the cumsum
  .derive({
    oneminus_cumsum: d => 1 - d.cumsum
})
  .derive({
     comparison_text: d => "Same as " + (op.round(d.proportion*100)) + "% of services of the same type, whilst " + (op.round(d.oneminus_cumsum*100)) + "% have a higher grade"
  })
  .filter((d, $) =>
    (d.kq === "KQ_Care_and_Support_Planning" && d.grade ===  $.selected_KQ_Care_and_Support_Planning) ||
    (d.kq === "KQ_Support_Wellbeing" && d.grade ===  $.selected_KQ_Support_Wellbeing) ||
    (d.kq === "KQ_Staff_Team" && d.grade ===  $.selected_KQ_Staff_Team) ||
    (d.kq === "KQ_Setting" && d.grade ===  $.selected_KQ_Setting) ||
    (d.kq === "KQ_Leadership" && d.grade ===  $.selected_KQ_Leadership) ||
    (d.kq === "KQ_Care_Play_and_Learning" && d.grade ===  $.selected_KQ_Care_Play_and_Learning)
  )
  
```

```{ojs}
// --- 3. Plot ---
Plot.plot({
  x: { axis: null, tickSize: 0, label: null }, // removes x-axis
  y: { tickSize: 0, label: null},
  marks: [
    // Big colored dots
    Plot.dot(selected_wrangled.objects(), {
      y: "kq_label",
      x: () => 0.05,
      fill: "grade",
      r: 45
    }),
    // Grade label inside dot
    Plot.text(selected_wrangled.objects(), {
      y: "kq_label",
      x: () => 0.05,
      text: "grade",
      fill: "white",
      fontWeight: "bold",
      fontSize: 12
    }),
    // Comparison text
    Plot.text(comparison_wrangled.objects(), {
      y: "kq_label",
      x: () => 0.35,
      text: "comparison_text",
      fontSize: 16,
      dy: -5
    })],
  x: {
    domain: [0, 1],
    axis: null,
    label: null,
    tickFormat: ""
  },
  color: {
    domain: grades,
    range: ["#d73027", "#fc8d59", "#fdcc3f", "#c3e648", "#91cf60", "#1a9850", "grey"],
    legend: false
  },
  style: {
    fontSize: "20px",  
    fontWeight: "bold",
    labelAnchor: "left"
    //fontFamily: "Open Sans"
  },
  width: Math.max(width, 800),
  height: 600,
  marginLeft: 700
})

```



