---
title: "Dashboard"
format:
  dashboard: 
    orientation: columns
---


## Column {width="20%"}

### Row {height="50%"}

```{r, install_packages}
#| echo: false
#| include: false
library(tidyverse)
```

```{r, load_data}
#| echo: false
#| include: false

raw_data <- readRDS("Data/2025-02-28_datastore.rds")


cleaned_data <-
  raw_data %>%
  # Select relevant columns
  select(
    CSNumber,
    ServiceName,
    CareService,
    Subtype,
    MinGrade,
    Last_inspection_Date,
    NumberStaff,
    Registered_Places,
    starts_with("KQ"),
    -ends_with("change"),
    Complaints_upheld_2425,
    Enforcements_issued_2425,
    any_requirements_2425
  ) %>%
  # Remove empty service ID numbers
  filter(CSNumber != "") %>%
  # Pivot grade categories in order to revalue grades as strings
  pivot_longer(cols = starts_with("KQ"),
               names_to = "Key Question",
               values_to = "Grade") %>%
  mutate(
    Grade = case_match(
      Grade,
      NA ~ "No grade yet",
      1 ~ "Unsatisfactory",
      2 ~ "Weak",
      3 ~ "Adequate",
      4 ~ "Good",
      5 ~ "Very good",
      6 ~ "Excellent"
    )
  ) %>%
  pivot_wider(names_from = `Key Question`, values_from = "Grade") %>%
  # Convert encoding to prevent special characters in strings
  mutate_if(is.character, function(col)
    iconv(col, to = "UTF-8"))

datastore <- 
  cleaned_data %>% 
  mutate(
    # Custom name for service combining with ID number
    service = paste0(CSNumber, " - ", ServiceName),
    # Converting minimum grade to strings too
    MinGrade = case_match(
      MinGrade,
      NA ~ "No grade yet",
      1 ~ "Unsatisfactory",
      2 ~ "Weak",
      3 ~ "Adequate",
      4 ~ "Good",
      5 ~ "Very good",
      6 ~ "Excellent"
    ),
    # Convert date fields to dates
    Last_inspection_Date = as.Date(Last_inspection_Date, format("%d/%m/%Y")),
    months_since_inspection = interval(Last_inspection_Date, Sys.Date()) %/% months(1),
    days_since_inspection = ifelse(
      months_since_inspection < 1,
      lubridate::time_length(difftime(Sys.Date(), Last_inspection_Date), "days"),
      NA
    ),
    years_since_inspection = lubridate::time_length(difftime(Sys.Date(), Last_inspection_Date), "years"),
    staff_per_place = ifelse(
      Registered_Places == 0 |
        NumberStaff == 0,
      NA,
      NumberStaff / Registered_Places
    )
  )

# Specify order of grades in minimum grade as factor
datastore$MinGrade <- factor(
datastore$MinGrade,
  levels =  c(
    "Unsatisfactory",
    "Weak",
    "Adequate",
    "Good",
    "Very good",
    "Excellent",
    "No grade yet"
  )
)
```


```{r, starwars}
x <- starwars
```

```{r, sendtoojs}
#| echo: false
#| include: false
ojs_define(service_name = x)
```

```{ojs}
//| expandable: false

// Transpose data to make it useable in ojs
service = transpose(service_name)

viewof search = Inputs.search(service, {placeholder: "Type to find a service",
width: 150,
height: 10})

viewof items = Inputs.table(search, {
columns: ["name"],
header: {name: "Care Service"},
width: 300,
height: 250,
required: false,
value: search, 
multiple: false})
```


```{ojs}
//| echo: false
//| output: false
function return_name() {
  var name = "Select a service"
  if(items === null) {
    return name
  } else {
    return items.name
  }
}

function filtered_df() {
  var name = "Select a service"
  if(items === null) {
    return name
  } else {
    return items
  }
}
```

### Row {height="50%"}

```{r, printstarwars}
head(x)
```

## Column {width="80%"}

### Row {height="20%"}
::: {.valuebox icon="pencil" color="blue"}
Service name

`{ojs} return_name()`

subtitle
:::

::: {.valuebox icon="pencil" color="blue"}
Service name

`{ojs} filtered_df().height`

subtitle
:::

::: {.valuebox icon="pencil" color="blue"}
Service name

`{ojs} filtered_df().mass`

subtitle
:::

::: {.valuebox icon="pencil" color="blue"}
Service name

`{ojs} filtered_df().hair_color`

subtitle
:::

### Row {height="20%"}

::: {.valuebox icon="pencil" color="blue"}
Service name

`{ojs} filtered_df().birth_year`

subtitle
:::

::: {.valuebox icon="pencil" color="blue"}
Service name

`{ojs} filtered_df().sex`

subtitle
:::


::: {.valuebox icon="pencil" color="blue"}
Service name

`{ojs} filtered_df()`

subtitle
:::


::: {.valuebox icon="pencil" color="blue"}
Service name

`{ojs} filtered_df()`

subtitle
:::


### Row {height="60%"}

`{ojs} filtered_df().name`

`{ojs} return_name()`



